|

### 2021-08-15 dissertation/msc_dissertation.Rmd
Further cleaning

---
title: |
  | __How analysis strategy affects analysis results__
subtitle: |
  | *Defining the results space in @silberzahn2018 through model specification*
  |
  | Master's thesis - DRAFT
author: "Sebastian Ploner, sploner1@sheffield.ac.uk, University of Sheffield"
linestretch: 1.5
output:
    pdf_document:
        includes:
            in_header: header.tex
        fig_caption: yes
urlcolor: blue
bibliography: references.bib
csl: apa.csl
header-includes:
  - \usepackage[ruled,vlined]{algorithm2e}
---

@@

knitr::opts_chunk$set(echo = TRUE)

@@

# Assign proper names for visualisation
long_df$variable = factor(long_df$variable,
                           levels = c("club", "victories", "weight_kg", "player_cards_received", "ties", "league_country", "specific_pos", "age_yrs", "ref", "ref_cards_assigned", "goals", "height_cm", "games", "ref_country", "player"),
                           labels = c("Club", "Victories", "Weight", "Cards rec.", "Ties", "Country", "Position", "Age", "Referee", "Cards assig.", "Goals", "Height", "Games", "Ref. country", "Player"))

# build plot
top = analysed_specifications %>% 
  filter(estimate_oddsratio < 4) %>% 
  ggplot(aes(as.numeric(id), estimate_oddsratio)) +
  geom_point(aes(colour = below_alpha), size = 0.3, alpha = 0.5) +
  geom_ribbon(aes(ymin = ci_lower_oddsratio, ymax = ci_upper_oddsratio), alpha = 0.3) +
  geom_hline(yintercept = 1, color = "black") +
  scale_color_manual(values = c("red", "black")) +
  scale_x_discrete(name = "", expand = c(0.01, 0)) +
  scale_y_continuous(name = "Odds ratio", breaks = c(seq(0.9, 1.7, 0.1)), limits = c(0.89, 1.71), expand = c(0, 0)) +
  labs(title = "Specification curve", subtitle = paste0("N = ", nrow(analysed_specifications), ", 95% CI", collapse = "")) +
  theme_classic() +
  theme(panel.grid.major.y = element_line(colour = "grey"),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.line.x = element_blank(),
        plot.margin = unit(c(0.5, 1, 0, 1), "cm"),
        legend.position = "top",
        legend.title.align = 1,
        legend.text = element_text(size = 11),
        legend.direction = "horizontal",
        legend.title = element_blank(),
        legend.margin = margin(t = -0.5, b = -0.2, unit = "cm"),
        legend.box.margin = margin(t = -0.5, b = -0.2, unit = "cm"),
        plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(face = "italic", margin = margin(0, 0, 20, 0)),
        text = element_text(size = 10)) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size = 1), reverse = TRUE))

bottom = long_df %>%
  ggplot(aes(x = id, y = reorder(x = variable, X = as.numeric(estimate_oddsratio)))) +
  geom_tile(aes(fill = below_alpha), width = 0.5, height = 0.5, color = "white") +
  scale_fill_manual(values = c("red", "black")) +
  scale_x_discrete(name = "Specifications", expand = c(0.01, 0)) +
  scale_y_discrete(name = "Covariates", expand = c(0.03, 0)) +
  theme_classic() +
  theme(legend.position = "none", 
        axis.ticks.y = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        plot.margin = unit(c(0, 1, 0.5, 1), "cm"),
        text = element_text(size = 10))

>>>>

---
title: |
  | __How analysis strategy affects analysis results__
subtitle: |
  | *Defining the results space in @silberzahn2018 through model specification*
  |
  | Master's thesis - DRAFT
author: "Sebastian Ploner, sploner1@sheffield.ac.uk, University of Sheffield"
linestretch: 1.5
output:
    pdf_document:
        includes:
            in_header: header.tex
        fig_caption: yes
urlcolor: blue
bibliography: references.bib
csl: apa.csl
header-includes:
  - \usepackage[ruled,vlined]{algorithm2e}
  - \usepackage{float}
---

@@

knitr::opts_chunk$set(echo = TRUE, fig.pos = 'H')

@@

# Assign proper names for visualisation
long_df$variable = factor(long_df$variable,
                           levels = c("club", "victories", "weight_kg", "player_cards_received", "ties", "league_country", "specific_pos", "age_yrs", "ref", "ref_cards_assigned", "goals", "height_cm", "games", "ref_country", "player"),
                           labels = c("Club", "Victories", "Weight", "Cards rec.", "Ties", "League", "Position", "Age", "Referee", "Cards assig.", "Goals", "Height", "Games", "Ref. country", "Player"))

# Covariates should be sorted based in their impact.
dat_covariates = dat_covariates[order(dat_covariates$estimate_oddsratio), ]
ordered_covar = dat_covariates$impact_names

# build plot
top = analysed_specifications %>% 
  filter(estimate_oddsratio < 4) %>% 
  ggplot(aes(as.numeric(id), estimate_oddsratio)) +
  geom_point(aes(colour = below_alpha), size = 0.3, alpha = 0.5) +
  geom_ribbon(aes(ymin = ci_lower_oddsratio, ymax = ci_upper_oddsratio), alpha = 0.3) +
  geom_hline(yintercept = 1, color = "black") +
  scale_color_manual(values = c("red", "black")) +
  scale_x_discrete(name = "", expand = c(0.01, 0)) +
  scale_y_continuous(name = "Odds ratio", breaks = c(seq(0.9, 1.7, 0.1)), limits = c(0.89, 1.71), expand = c(0, 0)) +
  labs(title = "Specification curve",
       subtitle = paste0("N = ", nrow(analysed_specifications), ", 95% CI", collapse = "")) +
  theme_classic() +
  theme(panel.grid.major.y = element_line(colour = "grey"),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.line.x = element_blank(),
        plot.margin = unit(c(0, 1, 0, 1), "cm"),
        legend.position = "top",
        legend.title.align = 1,
        legend.text = element_text(size = 11),
        legend.direction = "horizontal",
        legend.title = element_blank(),
        legend.margin = margin(t = -0.5, b = -0.2, unit = "cm"),
        legend.box.margin = margin(t = -0.5, b = -0.2, unit = "cm"),
        plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(face = "italic", margin = margin(0, 0, 20, 0)),
        text = element_text(size = 10)) +
  guides(colour = guide_legend(override.aes = list(alpha = 1, size = 1), reverse = TRUE))

bottom = long_df %>%
  ggplot(aes(x = id, y = factor(variable, levels = ordered_covar))) +
  geom_tile(aes(fill = below_alpha), width = 0.5, height = 0.5, color = "white") +
  scale_fill_manual(values = c("red", "black")) +
  scale_x_discrete(name = "Specifications", expand = c(0.01, 0)) +
  scale_y_discrete(name = "Covariates", expand = c(0.03, 0)) +
  theme_classic() +
  theme(legend.position = "none", 
        axis.ticks.y = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        plot.margin = unit(c(0, 1, 0.5, 1), "cm"),
        text = element_text(size = 10))
